\documentclass[oneside]{book}
\newcommand\deletechapter[1]{}

\title{The Extra}
\date{}
\author{\tiny
By Samuel Alexander\\\normalfont
\small
%\normalsize
    \parbox{0.8\linewidth}{\vspace{1in}``Would you rather be Zeus for a single day,
or see Zeus for the rest of your life,
only you can't tell anyone else you see him?''}}


\begin{document}

\maketitle


\chapter{Prophecy}

``All arise!''  All were eyes as the judge assumed the bench.  The crowds took their seats as the stenographer
read out the time:  ``Twenty four words.''  Proceedings were in session.

The plaintiff was the National Library,
suing for possession of an unpublished novel titled ``The Extra'',
written by the late Franz Kafka, who died of dehydration before he could
finish it.  The defendant was one Eva Koffe, daughter of Kafka's secretary
at the time of his death.  Representing both sides in their absense was Max Brod,
the friendless lawyer whose love of interest outweighed
the conflict of interest.

If Kafka had not been such a writer (the defense argued),
the Library would never have bothered to sue.
They would therefore base their defense on slandering ``The
Extra'' and its talentless hack of an author.  It was for this
reason the proceedings began with the
judge solemnly reading the book itself (organized
best as possible from Kafka's scattered scraps).

But before the judge could finish four paragraphs, a man in the audience stood up.
``Your honor,'' he announced uninvited, ``there must be some mistake, this book is
about me!''  ``Sit down!'' the judge ordered.  The man remained standing.  ``My name,''
he explained, ``is Joey Baloney.  Same as the character in that passage you read.
What's more, I match him perfect.  It must be some mistake I say again!''

``Who does this idiot think he is?!'' cried the defense's lawyer.
``Does he know how to behave in court?  Look at his outfit: talk about plain!
Why are these rifraff allowed in the city, much less in these halls?
Oh judge, make him sit down!''

``Get your butt in that seat,'' said the judge, unamused.  ``When you were born,
this author was dead.  I've heard of dying delusions, but we ain't in one.
It wouldn't make sense, there are computers and cellphones.
If your name is Baloney, it's purely coincidence.''   ``He's a liar,'' said Brod,
``you can't trust his name.''

``I agree with Brod,'' said the judge.  ``I know your type, Joseph, if that's really your name.
You rail against authority.  You would protest your own parents, if they had any power.
You're a lobbyist for people too lazy to pay you.
Hippy!  If you had your way, you'd turn our policemen to dust.''

``I will not sit down,'' said the man in the stands.  ``I can prove what I say.
I can prove it three times!  In fact you've given me the fifth, because all those
things you just said about me, you only know it cuz you read it in that book.''

``Enough,'' said the judge, with a wave toward the sergeant.
``See the gentleman out.''  ``Wait, judge,'' said Baloney.  ``If you have me
arrested, they'll check my ID, there'll be a paper trail proving I am who I am.''

``He's right,'' said Max Brod.  ``Oh drag!  Let's ignore him.  His feet will
wear out.  Sergeant, see to it that Joey Baloney can't use the water fountains.''
(At this the judge giggled.)  ``It's a hot day; let him stand in a desert.''

Just then, they were distracted.
Expert consultants were scheduled to make statements, and because their time
was important, they were to pop in, answer the judge's questions, and leave,
and not all at once, but spread through the week.

\chapter{Thirst}

One of the plaintiff's expert witnesses was a well-known professor.
He'd begun in analytic philosophy, and he'd won lifelong tenure.  But
after being tenured, he had some sort of religious experience.  He devoted
all his research, his studies, and even his intro freshman philosophy classes, 
entirely and single-mindedly to the subject of thirst.

This learned man had been summoned to stir
up sympathy for Kafka (who died of dehydration so painfully before finishing his novels),
and reduce the damage from the defense's slanderings.
``Good morning, professor,'' said Brod, ``I want to ask, if it's in your power, to
help this court understand, on a personal level, what it's like to die of thirst.''

``Certainly, m'lord.''  The professor opened his briefcase and papers poured out like sand.  ``I have prepared a story, your honor, which will help
the court understand.''

``Read it.''

\vspace{2mm}
\noindent \textit{The Professor's Story}
\vspace{2mm}

You're riding through Death Valley in a crowded, stinking bus.
You're going over the pass!
The air conditioning is shot, and it's hot inside.
Your companion has taken the final seat.
You're obliged to stand the whole ride, leaning down to participate in a conversation
which, for your companion's foreign accent, is full of strange idioms.

``Hey,'' you say leaning down, ``isn't this bus rather crowded?''

``Ja,'' says your companion, ``the crowd is like a river flooding into the bus.''

``Beautiful sunset this morning,'' you change the subject.

``Ja,'' comes the reply, ``happiness like a river flooding into my soul.''

You wipe your brow, the sweat has clammied up.
``I'm a bit thirsty.  Aren't you thirsty?''

Sad eyes return your gaze.
``Ja.  Like a river flooding into my mouth.''

\[*\mbox{ }*\mbox{ }*\]

``By the way, judge,'' said the professor departing.  ``Have you read my latest book, about dying in a desert
and hallucinating you're at home?''

``I have,'' said the judge.  ``You'll be happy to know my daughter adores it.
She re-enacts it day and night.  Wandering around the apartment making such a mess.
Crying for water but refusing to drink!''
%We can't get no sleep, and you're half to blame!''

``How old is your daughter, sir?''

``Eleven months old.''

\vspace{2mm}

A cacophany flooded through the hallowed halls.
The witness's testimony had made the audience thirsty,
but out of respect for the judge they refused to rise from their
seats.  One by one they scooted their chairs down side passages
to the court drinking fountains, and the sergeant at arms
checked every one to make sure it wasn't Joey Baloney.

\chapter{The Chairs}

The judge was reading from the manuscripts in a bored voice,
like a little boy in front of class.
%``The joker card represents villains because of its
%random, chaotic, unpredictable nature.
%``But imagine opening a
%deck and instead of finding a joker card, there's a dead rat: 
%weeks old,
%oozing with infection and crawling with maggots.
``That \emph{card} also represents a villain,
and that villain is Joey Baloney.''  
The judge frowned,
as if reminded of an overdue library book.

``Our chairs not good enough for you, then?''  He turned his glare toward
the Baloney in the stands.
``Sergeant, have we any better seats in these chambers?''

``No, your honor, they're the best we've got.''

``Well, the Senate's nearby, fetch some of theirs.''

The sergeant marched out of court and the judge leveled his gaze on Joey.
``Tell me again why you're standing, sir?''

``There's something amiss here,'' said Joey, ``that character in the book is me,
and that's quite impossible if it was really written by that author.
Even if you overlook the temporal impossibility---I was born after he
died---there's the fact I never gave persmission to use my likeness.''

``Well why didn't you say so?'' said the judge.  ``That's a very reasonable
complaint, we'll address it straight away!  Come, take a seat in the front,
your issue is our highest concern.''

Joey was too smart for that trap.  ``I ain't falling for your tricks,''
he said, ``I'll stand til my complaint is addressed.''

The judge was outraged.  He was going to shout some
mean things, when the sergeant returned to the courtroom.

``Here your honor, one of the best seats they got.  Seat of the Senate majority
leader.''  It was a giant seat, emblazoned with seals and surrounded by
desks and podiums, lesser seats for lesser senators.

``I will not sit,'' Joey said, turning his nose up at the furnishings.

``Alright, go get something better,'' said the judge.

The sergeant returned an hour later with a twisted silver chair, cold
to touch.  It hissed and slithered
like the beams were snakes.  Carved in back was a
hammer-and-sickle crossed-out with an X.  ``Hard to beat this one,'' said Sarge,
``the chair of no lesser figure than Senator McCarthy!''

``Won't sit, won't sit!'' Joey stuck out his tongue.

``Sergeant, stop playing around!'' cried the judge.  ``Don't come back til you've
found the finest chair in the Senate!''

At long length the sergeant returned.  He bore the chair Barack Obama
sat in before ascending on high.  It was crusted with gems and diamonds, some
big enough to be decked with smaller jewels.  It was draped in the finest
purple silks.
% of Persia, shimmering with an aura of priceless perfumes.

``Dear sir,'' said judge to Joey, ``this throne is yours, please accept your
coronation.  All you've got to do is sit in it!''

But Joey would not sit, even in that golden throne.
In despair, the judge had it melted down for scrap.

\chapter{The Drink}

A dozen witnesses had come, ignoring Joey Baloney like a statue.
(Several had been famous celebrities.  No relation
to the suit, but the judge considered
meeting celebrities a perk of the bench.)
The judge needed a break.  He declared a long recess.  Together with his lawyer,
stenographer, and sergeant at arms, he walked out of the chambers.
They reappeared through a little window looking out
on the playground.
%The judge began playing on the swingset.  Brod and the stenographer
%jumped on the see-saw, and the sergeant at arms went for the monkeybars.

Joey was thirsty, but gave no sign of wavering.
%To pass the time, he took a violin from his luggage and played awhile,
%a song mixing melancholy with joy.

In front of him there sat a young beauty.  If Joey was in a desert,
her beauty was his oasis.
She was almost perfect.  The only flaw was she'd slept wrong and a
strand of hair stood up awkwardly.
She turned in her seat and smiled.  ``I'm on your side,''
she offered.  ``I can't believe the injustice you're suffering.  The punishments the
judge has heaped on you.  What awful and lowly things the lawyers have said about you all day.''

``If I'm an awful and lowly man,'' Joey said, ``it's because I've stepped on the toes of giants.
I'm not resentful.''

``The defense attacked you so viciously,'' she said.  ``And you're innocent.
You're only trying to defend your likeness.  You're doing them a favor letting them know
something's wrong.''

``I am not resentful,'' Joey said.  ``I'm happy about it, it gave me the chance
to meet you.  What's your number?''

The young lady giggled, fingers playing with her hair.  ``My phone isn't on me, sir!
I do like you though.  I'm not just saying it to avoid exchanging digits.''

``I'd give you mine,'' Joey said, ``but the judge would say it's copyrighted.''

His partner smiled, offered her hand.  ``You're funny, Joey.  It's alright if I call you that?
Is Joseph better?''

``Joey is best,'' said Joey, alchemying the handshake into something tender.

``Joey is best,'' she repeated.  Then she laughed.  ``Talking with you makes me happy.
There's something playful about you.''   Joey broke the handshake moments before
she herself was going to.  ``I can't believe I'm saying it but you make the hairs stand up on
my arms.''

``Stand with me, we'll defy these tyrants together,'' offered Joey.

``I'm not as bold as you sir.  The only reason you're outside bars
is they're scared of proving your name.  My own is unimportant, they'd throw me in
jail for the both of us.''

``Stand by me, we'll live happily ever after,'' Joey haggled.

``Let's sit down together!'' she said.
Then in a suggestive register, ``I'll sit on your lap.''

Now Joey understood all.
%, and he knew the cruelty of his enemies.
``Off, whore!''  His demeanor changed.  ``I see what you are.
The court prostitute!  How much is the judge paying to sit me down?''

Tears welled in her eyes.
She liked Joey (he had a resemblance to her father, and it was growing stronger).
If he'd put her on his lap,
she'd have given him everything, would have sworn
her heart and soul to him, right hand on the bible.
Instead he held her in contempt.
His judgment crushed her like a death sentence.
She appealed with her eyes, but found no leniency.

``Then, I'll give you a present, for what might have been.''
She cupped her hands, she caught her tears, she lifted them toward him
from her seat.  Joey paused, caution versus thirst.
Caution down, he took her cupped fingers to his lips.
He drank up her tears.  They were delicious.  He swallowed and his thirst was cured.
%With leftover sobs, she
%leaned down (a difficult proposition from her position)
%and lovingly washed Joey's feet.

When no more tears would come, the maiden fled.
Out of respect for the judge, she crawled out on all fours.
%rather than stand up in his courts.




\deletechapter{

\chapter{The Foodfight}

A dozen witnesses had come by, ignoring Joey Baloney like a statue, and now the
judge needed a break.  He declared a short recess for lunch.  Together with the lawyer,
the stenographer, and the sergeant at arms, he walked out of the chambers.
A minute later, the four of them appeared through the little window that looked out
on the recess playground.  The judge began playing on the swingset.  Max and Franz
jumped onto the see-saw, and the sergeant at arms went for the monkeybars.

Inside the courthouse, the rustle of lunchbags was gradually drowned by a
growing murmer.  Spectators were arguing whether or not Joey Baloney really was the
same Joey Baloney from Kafka's unpublished novel.  They started forming little cliques,
and then little cliques swore alliances and turned into bigger cliques, and the volume
of the shouting grew.  Joey himself was the only man not arguing.

``Is that what you think?  Then why don't you take that egg and throw it at me?''
A handsome young man in a junior officer's service dress taunted a superior officer.
``Egg?'' came the retort, ``You can't handle egg!''  And then the egg flew threw the air.
This sparked a chain reaction and in moments, the entire courtroom was alive with
flying vegetables.

A piece of spiced tomato barely missed Atticus Finch's face.  Solemnly and with tremendous
patience, Atticus opened his shiny briefcase, took out a rifle, and loaded it with
garbanzo beans.  With steady, careful hands, like a surgeon, he took aim at his slavering enemy.
He pulled the trigger; suddenly his enemy was felled, chest splattered with chickpeas,
mouth frothing.

``Confound your logic!'' bellowed a famous prosecutor, throwing a handful of rice as if to
blind the opposing side.  ``I happen to know, from the head of a nursing home, this man who
calls himself Baloney didn't even cry at his own mother's funeral.  Is that a man you can
trust?''  He was silenced by a coldcut sandwich to the mouth.






(The court goes on lunchbreak (the court officials withdraw).  The audience starts fighting
over whether or not Joey is right.  This degenerates into a foodfight.  It turns out everyone
from the audience \emph{except} Joey is an important character from various fictional
court scenes.)
}

\chapter{The Stenographer}

``Did Kafka get his ideas by digging in graves?''

The defense attorney was deep in the throes of slandering the
deceased.  ``Kafka said he was Dostoevsky's blood brother.
If that's the case then who was the father?''

``Maybe they were half-brothers,'' the judge giggled.  ``A Russian and a German,
\emph{someone} was digging around!''  This drew childish laughter from the
audience, which pleased the judge tremendously.  Joey Baloney stood, refusing to
break his solemn filibuster.

``You're right, judge,'' laughed Brod.  ``Could explain where 'evsky got the idea for
Smerdyakov.  I always thought he looked the part.''

``If that's the case,'' chortled Judge, ``Kafka should've hanged himself.  Preferably
before writing this retarded book!''

``Next, your honor, I call the court's attention to Kafka's name.
What kind of name is Kafka?  It sounds like
something you'd buy at Starbucks.  `An iced
Kafka-latte.{'}''

``Objection\ldots''  Everyone turned toward the quiet source.
It was the court stenographer.

``Explain yourself!'' said the judge.  He wasn't used to objections in his court.

``Well,'' said the stenographer, ``I feel rather silly bringing it up, you know,
but I'd rather the kind Mr.~Esquire wouldn't bash Kafka's name.''

``Why not?!'' asked Brod, casting a hateful look on the poor typist as if it were Joey Baloney
himself.

``The thing is,'' said the stenographer, ``it's my name too.  Just a coincidence,
I assure you, no relation to the author.  I just don't think it's considerate
of you.  Maybe someone in the audience is named Kafka too.''

``Is there a Kafka on board?'' boomed the judge.
%, pointing his gavel at the great washed masses.
``Maybe you, mischief-maker?'' He looked now at Joey, as if Joey was an unwelcome bill at a restaurant.
``Still standing, are you?  How impolite I've been to my guest.  Have a seat, have a seat!  My wife will bring you snacks and
a beer.  Maybe you'd like a table to put your feet on?  Care to watch the telly?''

``No Kafkas today, sir,'' piped the sergeant at arms.  ``I'd know, sir, they're all regulars.
All but him I mean,'' with a nod at Baloney.

``Say, stenog,'' began the judge, ``Joey Baloney says he's in `The Extra'.  Does the manuscript
say how to make that character sit the hell down?''

``I wouldn't know, Judge.  I haven't read a lot of Kafka.  Actually nothing but the Metamorphoses, sir,
and that was ninth grade, sir.  You know they keep me too busy to read, sir.  I'm here doing my one-year
duty to pay off writing school debts, they don't give me a moment's rest, sir.''

``Don't like your job then?'' asked the judge.

``Not exactly sir,'' said the stenographer.
``I always thought I'd like writing, but now I'm doing it,
it's not for me.  All day I write down these bureaucratic proceedings.  Word after word.
Sometimes I ask myself: how many words 'til a man can be free?
To be honest sir, I only
come in any more to put bread on the table.  (My father calls it a \emph{Brodberuf}; that's
German, sir, for \emph{bread job}.)
So when the kind lawyer makes fun of my name, sir, it's insult on
injury, sir.''

``Man, I'm sorry, I had no idea,'' Brod apologized.  He crossed the floor and embraced the stenographer,
showing his sincerity.

``And it especially hurts,'' the stenographer went on through the embrace, voice cracking a little.
``Because recently I want nothing more
than to be a lawyer like you, Max.  The truth is, I have a great deal of admiration
for you, you've even inspired me to study law in my free time.''
Brod was genuinely touched.  It was a rare bonding moment, and the audience (all but Joey)
were moved.  Court historians would look back
for decades to come: the year Max Brod made his first friend.

The stenographer went on.  ``I hate to toot my own trumpet, but I've gained enough
lawyer's intuition I could say a thing or three about this Baloney case.''

``You don't speak much,'' the judge said.  ``But when you do it's
insightful.  Tell us about Baloney.''

The stenographer sized Joey up and down.  It took longer
than usual, there was more `up and down' to Joey than his seated peers.
``Well sir, contempt me if I'm wrong.  This man's the worst kind of anarchist.
Eats granola bars and protests polar bears.  He's an awful hipster, sir.
He's a communist sympathizer, but put him on the wall's other side and he'd sympathize
capitalist.  He---''

He was cut short by the judge's laughter.  ``You rascally little devil!'' the judge
declared.  ``Sergeant!  See to it the stenographer gets a \$20 bonus!''

``Thank you sir, but I don't know what you mean,'' said the typist.

``Don't know what I mean!''  The judge slapped his knees with the gavel.  ``You've read \emph{The Extra},
you've read it three times!''


\chapter{The Policeman}

The judge looked upon the rotting manuscripts, and drew his eyes away.
He looked upon the rotting court, and there stood Joey Baloney.

The next expert witness was Chief of Police.  The defense wanted his opinion on a certain
joke in ``The Extra''.  The assumption was that by getting the police to ridicule the work,
it would be slandered in the eyes of patriots.  As he entered, the Chief
shot a glare at the sergeant at arms, they were bitter rivals.

``Good afternoon chief, so glad you could make it,'' said Brod.

``Glad to be here, Brod,'' said the chief.  ``I understand you wanted to hear my opinion on a certain
piece of some book?''

``That's right,'' said Brod, ``but first I believe you had something to tell us about jokes in general?''

``Oh right!'' said the officer, remembering his coaching.  ``Listen judge.  You can't trust jokes.
They're like mafia fronts.  The mafia runs all these stores, and they sell you good stuff, but the goods aren't
the purpose.  There's sinister things done behind those stores.  It doesn't even matter if they
sell you anything at all.  Same thing with jokes.  Authors use them to hide things.  So it doesn't even matter
if the joke makes you laugh.  It doesn't even matter if it's funny.  There's sinister things done behind it,
and that's the joke's purpose.''

``Thanks,'' said the judge, ``I'll keep it in mind.''

``Now, chief,'' Brod directed, ``This unpublished book contains the following joke.  Tell us if it should
see the light of day.''

\vspace{2mm}
\noindent \textit{The Joke}
\vspace{2mm}

Knock knock.  The apartment's got couches, but the intruder ain't here to sit.

It's a policeman.  He's thin, in the bad way.
Tall like a stick.  Looks unhappy to be there.  Miserable, even.  You can tell he'd
rather be anywhere in all the world than at this apartment.  He'd pay any price to just
get away.

``Sir,'' he says, ``We've received a complaint from your wife, says you're not having enough fun.''

Just then there's a crash down the hall.  The policeman's wife has arrived.  She's ugly and mean: who would
ever marry her?  She's berating the poor cop, shouting at him for harassing the poor man, for being
such a wet blanket.

\[*\mbox{ }*\mbox{ }*\]

``Stop!'' cried the chief, boiling with rage.
``Never have I heard such damnable garbage.
I've heard quite enough!  This Kafka fellow, why, he just ain't American.''

He spun toward the stenographer and suddenly demanded:  ``How much longer
is the stupid thing anyway?''  Caught off guard, the stenographer was
struck dumb.

An idea occurred to the chief.
``Yo, judge, here's what you should do.  Make this damned \emph{Extra} be the Book
of Jafar.''

``The Book of Jafar?'' asked the judge, eyebrow raised.

``You don't know it?'' said Chief.  ``Oh, you'll like it, I'm sure!
Once upon a time, there was a wizard named Jafar.
Jafar was great, every book he wrote sold wide.
Jafar got fed up.  He hated that fame.  Used all his
arts, and used all his powers, and crafted a magical book of obscurity.
A book enchanted with spells so that no-one would read it, or even know
it existed.  And you know what?  It worked.''

There was a crash in the hall.  The police chief's wife had arrived.
The stenographer finally recovered and answered the question:
``The chapter's unfinished.''

\chapter{Intermission}

Many words had been exchanged in the court, and it was late.
Or maybe early: hard to say without studying the
transcripts.  Around the bleachers, jurists slept in their seats.
Some had brought sleeping bags, and were
sprawled out in the aisles, but no-one dared stand, no-one but
Joey.  An amorous purr drifted from somewhere in back of the
hall.  Joey yawned and rubbed
his eyes.

An old man on the balcony was eating a bag of
chips, and his crumbs flittered into the stands.
Crusty particles burned Joey's eyes and he
nodded off, dozing on his feet.

In an uneasy nap the words of the court were mixed up and
scrambled, and Joey dreamt two dreams, interdependent opposites
woven like a rope of snakes.

\vspace{2mm}
\noindent \textit{Joey's Two Dreams}
\vspace{2mm}

I was right in the middle of my speech.
``The joker card represents villains because of its
random, chaotic, unpredictable nature.  But imagine opening a
deck and instead of finding a joker card, there's a dead rat:
weeks old,
oozing with infection and crawling with maggots.  That \emph{card} also represents a villain,
and that villain is Joey Baloney.
I met him in a glass elevator, the only other occupants were a little boy and his mother.
Joey whipped it out of his pants and began pissing in the corner.  He was raving like a lunatic,
informing the boy, in quick and feverish narratives, where babies come from.''

Among my audience I saw worried glances and confusion.  I'd been invited to this renowned conference
to present my research.  And here I was, telling them about Joey Baloney.
Instead of sterile academia, I was unveiling a grander truth, forbidden,
the world was not ready for it.
A speech that would see me in jail or dead by night's end.

``Joey Baloney's words rushed out in breathless rapidity, he was struggling to tell the
boy everything he could about human reproduction before I could stop him.
I was a policeman back then.  Used to dealing with crazies on the elevators,
but nothing like Baloney.
I stood gaping for a few seconds.  Precious time for Joey Baloney to continue his shpiel.''

I saw the looks turning to panic.  Famous gatekeepers of knowledge wondering if I'd lost my
marbles.  I'd have to hurry if I were to deliver this truth before the front row would
rush and tackle me.

``The mother shrieked for help.  My ears rang, with trembling hands I leveled the tazer, I fired.
Joey Baloney fell to the ground, lay in his own steaming urine, and yet his monologue continued!''

Women were fainting now in the audience, cries of panic in the back.
Colleagues were rushing to them, make room make room!, pleas falling on deaf ears
as distinguished professors sat transfixed.
The first to rush me was a war veteran, a Harvard dean who'd
killed twenty Germans with his bare hands.
He stumbled, fell.

``The boy was sobbing, unprepared for the vulgar knowledge.
I threw the tazer aside, grabbed my firearm, whipped it out of my pants,
shot Baloney in the head!  The elevator shattered.''

I shouted into the mic to subdue the rising protests.
Career suicide, that's for sure, but more than that, it was real suicide.
There are truths which must not be spoken to those who do not know them.
Truths that shatter innocence, that complicate the carefree world.
I know things that'd make your mother cover your ears.
Things so astounding they'd put me to death.
And here I was, shouting them: to a man like me, truth
is more important than breath.
A giant in the world of womens' studies threw herself at me.
I brandished the mic, I thrust it into her crotch, I stamped on her toes.
Don't stop me now!

``Joey Baloney has gone by many names.  Genghis Khan; Hitler.''
I kicked a Fields medalist as he lunged for the mic.  Our fathers
died for freedom, a few ivory towerists can take a kick for truth.
You see, some truths are so forbidden, even if you want to tell them
you can't.  You have to tell something else instead, something silly or obvious or both,
a stand-in.  Those in the know will understand.
Sign of solidarity, reinforce the besieged truth.

``The ancients referred to him as Loki, great trickster.''
I ducked just in time to dodge the first hail of bullets.
Amazing how the authorities rush when the status quo is
really threatened.
``He's the type who invents new kinds of crimes just for the novelty.
Like take someone else's writing, pass it off as his own, and make
it public domain, just to cause trouble.''
%He'd take this very speech itself, and say: This work is
%released into the public domain.  Even though it's certainly
%not!'' 

A dozen SWAT commandos tackled the podium.
An assault rifle blasted my brains all over the conference hall.
And yet with labored breaths I went on.
(It's funny, I felt no pain, only thirst.)
Only the riot police heard me any more, but that's alright,
because you hear me, and you will hear me to the end, even if your mother
doesn't want you to.  No-one will deny you this fruit of the tree.
``I was unconscious briefly after we fell from the elevator.
When I came to, Joey Baloney was whispering to the boy with labored breaths,
though only I could hear him anymore.''
%I wasn't dead, because no-one knows what's after death.
%By which I mean, the unknownness is part of the \emph{definition},
%not just a side effect.  The first man whose afterlife we know about, will never die because we'll
%remember him eternally.  The point is, I do know what comes after, though that's not the
%knowledge I mentioned earlier, it's just a footnote in fact.

``For years, people would imitate Joey Baloney, exposing themselves to children
and shouting unwelcome biology.  Like Joey, they'd always introduce themselves:
Ladies and Gentlemen, Joey Baloney!  It got so bad the government built
hemlock drones to shoot whoever said that phrase.''

``But after time, thanks to the drones, people forgot what was even supposed to come
after the Ladies and Gentlemen, Joey Baloney.  It was a conundrum, the
whole point was to stop the transmission of that forbidden knowledge,
now that no-one remembered it, was it still legal for the drones to shoot them?
In the end it became a crime punishable by death to even imagine what Joey
said after his introduction.
But what the imposters were supposed to say, what Joey Baloney said after his
introduction, went like this\ldots''

I'm too weak to speak aloud now, no time to finish.
No time to present my proof that Joey was there at the start:
He whipped a rib out of Adam's pants, he stuck it in Eve, and that's where
babies come from.  The important thing is, I know.
Remember that if you know nothing else about me: I know.
%, if you know nothing about what happens
%to me after my death: I know.

``A hush came over the conference as the speaker lay in his own steaming blood.
By sheer force of habit, the organizer picked up the microphone and uttered the
outro.''  Ladies and Gentlemen, Joey Baloney.


\chapter{The Judge's Speech}

``How many words will it take, before our policemen turn to dust?''

The judge was infinitely exasperated at Joey Baloney's stand,
charging his speech with feeling.
%Bloodless fingers clutched the podium.

``How many words will it take before old men bow down to the wisdom
of boys?
%How many words until joy replaces terror in the hearts of the world?''
How many words until schools let out early, and teachers make a decent wage?
How many words `til lambs lie down with lions?''


%As he spoke, the judge's words seemed to project lofty images in the hearts of the court,
%sprawling panoramas of human nature and all its faults.
``How many words will it take
before unemployment protestors are laid off?
How many words until the meek demand their inheritance?
How many sentences must this court deliver before this court's sentences are obsolete?''

``How many words will it take, til every dissenter assents?  How many words will it take,
to replace warfare with wars of words?  Fold swords into pens?
How many words til green fields and rivers
blossom in Death Valley?
How many words will it take `til
colonies are uprooted and native kings restored?  `Til pharmacies are replaced
by shamans?  `Til propaganda is dragged through the mud?  How many words will it take?''

``How many words, Joey, if that is your name, until capitalists pay for their greed?
How many words must this court spend before mankind lives as one?
How many words must you steal from this court,
Joey, before man stops stealing from man?  How many words must the courts print before
the chains of copyright come off?  How many words til cars turn into bikes
and soldiers return home?''

Elder statesmen wept and young activists trembled.
``How many words must this battle go on?
How many words will it take to satisfy people who demand to be offended?  How many Kumbaya's
`til every Baptist is Buddhist, `til Muslims join Womens' Lib?
How many words must we trade before stock markets turn to farmers
markets?
How many words before the weapons that end wars will end?''

A tear gathered in the corner of the judge's eye, growing until the gravity of
his words loosed it.
It caught a holy ray of light in its fall,
bending every lawyer in the court to weep openly.
Every woman covered her face.
And still the judge's speech went on, the light in his eye blinding every clerk.

``How many words til civil wars become civilized? 
How many words til history's wrongs are righted and its rights distributed equally?
How many words until high school students read willingly, 
and Satan ceases his ceaseless sieges on God?''

The courthouse shook.
The universe paused its weary
acceleration, a moment of respectful silence in the cosmic background radiation.
The judge lifted his gavel, he pounded the dais,
damn the protocols, use it just for emphasis.  The gavel's head broke off,
the judge tossed the handle and raised a fist to heaven.
``How many words, `til our policemen turn to dust?''

Joey sat.



\end{document}
