\documentclass{memoir}

\title{Joey Baloney}
\author{A short work of fiction by Samuel Alexander}
\date{}

\begin{document}

\maketitle

I was right in the middle of my speech.  ``The Joker card can play any role in a deck.
It represents a chaotic, unpredictable villain.
But imagine you open a pack of cards and instead of a joker, you find a dead rat: weeks old,
oozing with infection and swarming with maggots.  That \emph{card} also represents a villain,
and that villain is Joey Baloney.  I met him in a glass elevator, the only other occupants were
a very young boy with his frail old mother.
Joey Baloney whipped it right out of his pants and began pissing
in the corner.  He was raving like a lunatic and informing the boy, in quick and
feverish narratives, where babies come from.''

Among my audience I saw the worried glances and the confusion.  I'd been invited to this renowned
conference to present my groundbreaking work on G\"odelian syntax.  And here I was,
telling them about Joey Baloney.  I had promised some sterile academic theorem to them.
And instead here I was, unveiling a far grander truth, a forbidden truth, a truth
the world will never be ready for.  Delivering a speech that would probably see me in jail or
dead by night's end.  

``Joey Baloney's words rushed out in breathless rapidity, he was struggling to tell the little boy
everything he could about human reproduction before I could stop him.  I was a cop back then, you see.
I was used to dealing with crazies on the elevators, but never anything like Joey Baloney.
I stood there gaping for a few seconds, too shocked to move.  Precious time for Joey Baloney to
continue his shpiel.''

I could see the worried looks turning to panic, famous gatekeepers of human knowledge wondering
if I'd lost my marbles.  I would have to speak faster if I were to express this game-changing truth
before the Nobel laureates in the front row could figure out my schtick and tackle me. 

``The boy's mother was shrieking for help, for someone to do something.  My ears were ringing.
With trembling hands I leveled the tazer.  I fired.  Joey Baloney fell to the ground, lay
in his own steaming urine, and yet his monologue continued!''

Women were fainting now in the audience, and there were cries of panic in the back.
Colleagues from the medical school were rushing to them, begging people to make room,
their pleas falling on deaf ears as distinguished professors sat transfixed.
The first Laureate to make his move was a grizzled war veteran, a dean of Harvard who had
killed twenty Germans with his bare hands.  He rushed toward me,
stumbled, fell, just as he fell when that German machine gunner finally stopped him and gave
him his purple heart.  

``The boy was sobbing, unprepared for the vulgar knowledge unleashed by Joey Baloney.
I threw the tazer aside, I grabbed my firearm, I whipped it right out of my pants, I shot
Joey Baloney in the head.  The elevator shattered.''

I had to shout into the microphone to subdue the protests rising from
the crowd.  It was career suicide, that's for sure, but more than that, it was real suicide.
You see, there are truths which must not be spoken in the presence of those who do not
know them already.  Truths that shatted innocence, that turn a carefree world complicated.
I know things that would make your mother cover your ears.  I know things so astounding that
if I told them, I'd be put to death.  And here I was, telling them, because to a man like me,
truth is more important than breath.

``Joey Baloney has gone by many names.  Genghis Khan.  Hitler.  Humphrey Appleby.
Fyodor Karamozov.  He spent awhile as Alan Greenspan, telling people:  everything is
acceptable as long as house prices don't crash.''  I kicked a Fields medalist violently
in the chest as he lunged for the mic.  Our forefathers died for freedom, a few of these
ivory towerists can take a kick for truth.  You see, some truths are so forbidden, that
even if you want to tell them, you can't.  You have to tell something else instead, something
silly everyone already knows, as a stand-in.  But those who are in the know, will see that
you are in the know.  A sign of solidarity, to encourage the truthholders to hold out until
our numbers have grown enough that we can toss aside the symbols for the real deal, the
jokers for the villains and the dead rats for the Joey Baloneys.

``The ancients referred to Joey Baloney as Loki, the great trickster.''  I ducked behind the
podium just in time to dodge the first hail of bullets.  Amazing how fast the authorities arrive
when the status quo is really threatened.  ``He's the kind of man who will take someone else's
writing, pass it off as his own, and then declare it public domain.  Why, he would take this
very speech I'm making now, and declare.  This work is released into the public domain.''
Just to be entirely clear, of course, this work is most certainly Copyright 2014.  The microphone
stopped.  Someone had cut the power to it.  I lifted my voice, and screamed, screamed my story
above the cacophany.

``Joey Baloney's the kind of man who would sprinkle other peoples' phrases in his own books,
plagiarised and unattributed, but then include a passage explicitly saying as much, saying it's
the twenty-first century and people can find who he's quoting by searching the net.  Then the
legal system's all set amuck trying to figure out whether he really plagiarized or not.  Murderers
walk free as judges pull their hair out.''  The microphone useless now, I spun it around as an
improvised weapon, a flail to beat off the waves of academics rushing now to stop me.

``He was president once.  Of the united states.  A president, babbling all this nonsense on
TV, a billion viewers learning where babies come from, live on CNN.''  A butch sociologist got
up too close for comfort.  I thrust the stiff microphone into her crotch, guided by a biological
imperative to finish my speech.

``I was in the Secret Service then.  We were afraid he would
rewrite the Constitution, make himself president for all future time.  He did something worse.
He rewrote it a different way, made himself president for all \emph{past} time.  So when Roosevelt
nuked Dresden, that wasn't Roosevelt.  That was Joey Baloney.  I was there, you know, in Dresden
I mean.  Dancing in a nightclub called \emph{The Station}.  Its nuking was caught on tape, you can
look it up if you have a strong stomach.  When Truman firebombed Hiroshima, that was Joey
Baloney too.  And I was there, too, listening to Great White, their lead guitarist
died in the firestorm.  Trail of Tears?  Joey Baloney.  He made himself responsible for
every injustice this great country every achieved.  Joey Baloney died for their sins, those politicos
too sinful for Jesus Christ.''

A dozen SWAT commandos tackled the podium, tackling me with it.
A high-powered assault rifle blasted my grey matter all over the conference hall.
And yet with labored breaths I went on.
Only the riot police could even hear me, but
that's not important, because you hear me, and you will hear me to the end, even if your parents
don't want you to.  Even if they don't want you to savor this fruit of the tree I tempt you with.
``I was unconscious briefly, after we all fell from that shattered elevator.  When I came to, Joey Baloney
was whispering to the boy with labored breaths, though only I could even hear him anymore.''  I wasn't dead, because
no-one knows what's after death.  By which I mean, the unknownness is part of the \emph{definition} of death,
not just a side effect.  The man whose afterlife we know about, will never die because we'll remember him
eternally.  And the point is, I do know what comes after death, although that's not the knowledge I told you about earlier,
it's just a side effect.

``For years, people would imitate Joey Baloney, exposing themselves to children and bludgeoning them with
unsolicited biological knowledge.  Like Joey Baloney, they'd always introduce themselves first: Ladies and Gentlemen,
Joey Baloney!  It got so bad the government built drones to shoot anyone who said that phrase, before they could
proceed.  Hemlock drones they were called, the solution to the corruption of the youth.''

``But after time, because of the Hemlock drones, people forgot what was even supposed to come after the Ladies and Gentlemen, Joey Baloney.  And then it was a terrible conundrum, because the entire point was to
pre-emptively stop the transmission of that forbidden knowledge, and now that no-one remembered it, was it or was it not legal for the drones to shoot those imposters?  The legal system was all set amuck trying to figure it out.  Murdered walked free as judges pulled their hair out.
In the end, it become a crime punishable by death merely to \emph{know}
what Joey Baloney said after his introduction.
But what the imposters were supposed to say, what Joey Baloney said after his introduction, went like this...''

I'm too weak to speak aloud any more, and there's no time to finish.
No time to present my proof that Joey Baloney was there at the very beginning:
that He took out a rib from between Adam's legs, and put it in Eve, and that's where babies come from.
The important thing is:  I Know.  Remember that if you remember nothing else about me, if you know nothing about what happens to me after my death:  I Know.

``A great solumn hush came over the conference hall as the speaker
lay in his own steaming blood.  Pushed by sheer force of habit, from running a dozen conferences in his time as chair of the society, the most iminent scholar of the room stepped forward, trembling as if in shock, he picked up the dead microphone and spoke into it the standard phrase to signal the end of the speech.''  Ladies and Gentlemen, Joey Baloney.

\end{document}
